The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-15 article.tex
Fixed whitespace

    \begin{minipage}{1\textwidth}
    \centering
    \begin{tabular}{llllllll}
	\multirow{2}{*}{ Mass (Da) } & \multirow{2}{*}{ Tolerance ($\pm$ Da) } & \multicolumn{3}{c}{ \# of generated formulas } & \multicolumn{3}{c}{ Runtime (s) } \\
	& & HR2 & PFG & CDK & HR2 & PFG & CDK \\
	\multirow{2}{*}{ $100$ } & $0.001$ & $1$ & $1$ & $1$ & $0.10$ & \textbf{$0.06$} & $0.49$ \\
	& $0.01$ & $18$ & $18$ & $18$ & $0.03$ & \textbf{$0.01$} & $0.52$ \\
	\multirow{2}{*}{ $500$ } & $0.001$ & $430$ & $430$ & $430$ & $0.51$ & \textbf{$0.09$} & $0.67$ \\
	& $0.01$ & $4\,265$ & $4\,265$ & $4\,264$ & $0.55$ & \textbf{$0.39$} & $0.96$ \\
	\multirow{2}{*}{ $1\,000$ } & $0.001$ & $8\,572$ & $8\,572$ & $8\,568$ & $16.5$ & $1.5$ & \textbf{$1.2$} \\
	& $0.01$ & $85\,542$ & $85\,542$ & $85\,537$ & $16.8$ & $5.4$ & \textbf{$3.7$} \\
	\multirow{2}{*}{ $2\,000$ } & $0.001$ & $226\,346$ & $226\,346$ & $226\,323$ & $1156.5$ & $58.9$ & \textbf{$8.6$} \\
	& $0.01$ & $2\,263\,410$ & $2\,263\,410$ & $2\,263\,409$ & $932.5$ & $156.3$ & \textbf{$69.7$} \\
	\multirow{2}{*}{ $3\,000$ } & $0.001$ & $1\,647\,132$ & $1\,647\,132$ & $1\,647\,118$ & $9\,667.9$ & $603.5$ & \textbf{$59.3$} \\
	& $0.01$ & $16\,471\,338$ & $16\,471\,338$ & $16\,471\,373$ & $9\,694.5$ & $1\,303.6$ & \textbf{$505.7$} \\
    \end{tabular}
    \end{minipage}

>>>>

    \begin{minipage}{1\textwidth}
    \centering
    \begin{tabular}{llllllll}
	\multirow{2}{*}{ Mass (Da) } & \multirow{2}{*}{ Tolerance ($\pm$ Da) } & \multicolumn{3}{c}{ \# of generated formulas } & \multicolumn{3}{c}{ Runtime (s) } \\
	& & HR2 & PFG & CDK & HR2 & PFG & CDK \\
	$100$ & $0.001$ & $1$ & $1$ & $1$ & $0.10$ & $\mathbf{0.06}$ & $0.49$ \\
	$100$ & $0.01$ & $18$ & $18$ & $18$ & $0.03$ & $\mathbf{0.01}$ & $0.52$ \\
	$500$ & $0.001$ & $430$ & $430$ & $430$ & $0.51$ & $\mathbf{0.09}$ & $0.67$ \\
	$500$ & $0.01$ & $4\,265$ & $4\,265$ & $4\,264$ & $0.55$ & $\mathbf{0.39}$ & $0.96$ \\
	$1\,000$ & $0.001$ & $8\,572$ & $8\,572$ & $8\,568$ & $16.5$ & $1.5$ & $\mathbf{1.2}$ \\
	$1\,000$ & $0.01$ & $85\,542$ & $85\,542$ & $85\,537$ & $16.8$ & $5.4$ & $\mathbf{3.7}$ \\
	$2\,000$ & $0.001$ & $226\,346$ & $226\,346$ & $226\,323$ & $1156.5$ & $58.9$ & $\mathbf{8.6}$ \\
	$2\,000$ & $0.01$ & $2\,263\,410$ & $2\,263\,410$ & $2\,263\,409$ & $932.5$ & $156.3$ & $\mathbf{69.7}$ \\
	$3\,000$ & $0.001$ & $1\,647\,132$ & $1\,647\,132$ & $1\,647\,118$ & $9\,667.9$ & $603.5$ & $\mathbf{59.3}$ \\
	$3\,000$ & $0.01$ & $16\,471\,338$ & $16\,471\,338$ & $16\,471\,373$ & $9\,694.5$ & $1\,303.6$ & $\mathbf{505.7}$ \\
    \end{tabular}
    \end{minipage}
